---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# fars
![Travis Badge](https://travis-ci.org/yzhang3142/fars.svg?branch=master)

## Overview

This package is created as part of the assessment for the course Building R
Packages on Coursera.

## Installation

You can install rpkgtutorial from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("yzhang3142/fars")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval = FALSE}
fars_summarize_years(c(2013, 2014))

fars_map_state(4, 2013)
```

## Evaluations

* Does this package contain the correct R file(s) under the R/ directory?
* Does this package contain a man/ directory with corresponding 
documentation files?
* Does this package contain a vignette which provides a meaningful description 
of the package and how it should be used?
* Does this package have at least one test included in the tests/ directory?
* Does this package have a NAMESPACE file?
* Does the README.md file for this directory have a Travis badge?
* Is the build of this package passing on Travis?
* Are the build logs for this package on Travis free of any errors, 
warnings, or notes?
